### 2016-08-31 version0.0/paper2.tex
Update paper2.tex
minor grammar change
change line 567 of chapter 4, to include S.G.'s comment on the other type of galaxies that are not in the K96 template

            Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
            In these plots we force the galaxies to be categorized in a maximum 3 groups. 
            If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
            However, in the lower panel of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two templates.
            These two templates, which are separated from the group of starburst templates in the lower part of Fig.~\ref{fig: 1by2T},  are the SB5 and SB6 types.
            In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
            The black colour indicates that the left neuron is completely different from the other two groups,
            while the white colour shows that the two right neurons are very similar to one another.

@@

    \subsection{Two-Dimensional Self-Organizing Maps}
    \label{sec: 2D}
    The one-dimensional networks are great tools to categorize the spectral types of galaxies and monitor the changes of properties of galaxies with category.
    However, each neuron in these networks is limited to be connected to one other neuron in each direction.
    In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete pictures of relations between each spectral type.
    As described in Section~\ref{sec: method_somz}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
    This quality of the SOMs provides a unique opportunity to analyse 2D networks using two approaches. 
    At first, as in the 1D SOMs, we assumed that all the galaxies must have spectra similar to any of the 12 templates in Fig.~\ref{fig: k96}.
    In this case, we can categorize spectra of other galaxies based on those 12 types.
    In the second approach, we trained networks with the assumption that there might be completely different types of galaxies not encountered before.
    This approach can be used to trace and recognize the outliers, which could include galaxy types that are not presented in the \citetalias{Kinney96} templates.
    To execute the second approach, we used the {\textsc selforgmap} library in the {\textsc matlab}.
    Unlike the {\textsc newsom} library which the ordering step neighbourhood distance is set by default (although in an SOM it should be a free parameters), in the {\textsc selforgmap} we can change this value.
    Using the {\textsc selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together, allowing room for outliers.

>>>>

            Fig.~\ref{fig: 1by3T} shows the results of the training in a 1$\times$3 network.
            In these plots we force the galaxies to be categorized in a maximum of 3 groups. 
            If the templates in Fig.~\ref{fig: 1by2T} truly belonged in two groups, they would be grouped into two groups in this network, even when we try to cluster them into three. 
            However, in the lower panel of Fig.~\ref{fig: 1by3T}, we can see that the middle node contains two templates.
            These two templates, which are separated from the group of starburst templates in the lower part of Fig.~\ref{fig: 1by2T},  are the SB5 and SB6 types.
            In the upper plot of Fig.~\ref{fig: 1by3T}, the colour between two right neurons is black and the colour between two left neurons is white. 
            The black colour indicates that the left neuron is completely different from the other two groups,
            while the white colour shows that the two right neurons are very similar to one another.

@@

    \subsection{Two-Dimensional Self-Organizing Maps}
    \label{sec: 2D}
    The one-dimensional networks are great tools to categorize the spectral types of galaxies and monitor the changes of properties of galaxies with category.
    However, each neuron in these networks is limited to be connected to one other neuron in each direction.
    In a 2D network, each neuron can have more than two immediate neighbours, providing a more complete pictures of relations between each spectral type.
    As described in Section~\ref{sec: method_somz}, one of the main advantages of the SOM is that when the weight of one neuron is adjusted after finding the best matching unit, the weight of the whole map will be changed.
    This quality of the SOMs provides a unique opportunity to analyse 2D networks using two approaches. 
    At first, as in the 1D SOMs, we assumed that all the galaxies must have spectra similar to any of the 12 templates in Fig.~\ref{fig: k96}.
    In this case, we can categorize spectra of other galaxies based on those 12 types.
    In the second approach, we trained networks with the assumption that there might be completely different types of galaxies not encountered before.
    This approach can be used to trace and recognize the outliers, which could include galaxy types that are not presented in the \citetalias{Kinney96} templates (e.g. dwarf galaxies, luminous infrared galaxies, active galactic nucleus).
    To execute the second approach, we used the {\textsc selforgmap} library in the {\textsc matlab}.
    Unlike the {\textsc newsom} library which the ordering step neighbourhood distance is set by default (although in an SOM it should be a free parameters), in the {\textsc selforgmap} we can change this value.
    Using the {\textsc selforgmap} code, based on the size of a map and the ordering step neighbourhood distance, we can arrange that the data spread all over the SOM or sit close together, allowing room for outliers.
